Twisted 11-dimensional supergravity, I

### 2021-08-25 draft.tex
g2

>>>>

\parsec[sec:nmsymmetry]
Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.

We start with the global symmetry algebra $E(5,10)$ of the holomorphic twist of the 11-dimensional theory. 
From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
\begin{align*}
[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
\end{align*}
where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.

From these relations, it is easy to see that any divergence-free vector field of the form:
\begin{itemize}
\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
\end{itemize}
are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.

Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
\[
H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
\]
Notice that on $\CC^2$, there is an exactly sequence of Lie algebras
\[
0 \to \ul\CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
\]
where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$:
\[
[f(z_1,z_2) , g(z_1,z_2)] = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
\]
